Measuring starspot properties by forward modeling IGRINS spectra of \name

### 2016-07-01 document/ms.tex
Add new Figures about Two Temp results and fill factor, many-panel figure of spectra for all orders, Table content

\subsection{Result 12: Signal from deriving $\teff$ in each IGRINS order}

@@

\subsection{Result 22: Direct measurement of spot properties with mixture model}

Figure XX shows the joint posterior probability density distribution of $\teffb$ versus $f$ calculated independently for $N_{ord}=25$ IGRINS orders.

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/Star_spot_measurement} 
	\caption{Effective temperature as derived by different orders.}
	\label{fig:StarspotProperties}
\end{figure*}

@@

>>>>

\subsection{Na\"ieve Single Component spectral fit to each spectral order}

@@

\subsection{Two-temperature photophere model fit to each spectral order}

Figure \ref{fig:TwoTempResults} shows the starspot and photospheric temperature derived independently for 43 IGRINS orders.
%% Things to say:
% - Range of allowed temperatures and assumptions for each run
% - H-band is tight
% - Scatter in $K-Band$
% - Telluric lines and other artifacts in the data
% - Metal lines affected

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/LkCa4_HK_mixTeff_by_order} 
	\caption{Two-temperature model properties, $\teffa$ and $\teffb$, derived independently from full-spectrum fitting 43 IGRINS orders.  The top panel denotes typical telluric transmission for all of the possible 54 IGRINS orders.  The derived effective temperatures show enhanced scatter in $K-$band.}
	\label{fig:TwoTempResults}
\end{figure*}

%% Plot of all spectra (vis-a-vis the poster)
%(In the appendix for now)
%% Things to say:
% - Systematics-dominated traps
% - Metal lines, and derived [Fe/H]
% - Calibration artifacts
% - Nice agreement
% - Not every order has strongly temperature-sensitive lines
% - Orders with very strong lines at one temperature will dominate

\begin{figure*}
	\centering
	\includegraphics[width=0.39\textwidth]{figures/LkCa4_fill_vs_Teff2} 
	\caption{Joint constraint on the temperature of starspots $\teffb$, and their observed solid-angular filling factor $f$.  Each data point and error bar are taken from Table \ref{tbl_order_results}, with the error bars therefore representing 2$\sigma$ errors.}
	\label{fig:TwoTempResults}
\end{figure*}

%% Plot of starspot fill factor vs. Teff2
%% Things to say:
% - Many ways to combine the posteriors
% - "Observed" fill factor
% - Scatter
% - Large range in fill factor is like adding a DC component and renormalizing

@@

\section{Examples of full spectrum fitting}

Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} show spectra from 42 IGRINS orders.

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/H_band_spectra_3x7}
	\caption{IGRINS Orders 94 and $99-119$.  Note that the $y-$axis is on a logarithmic scale.  }
	\label{fig:Hband3x7}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/K_band_spectra_3x7}
	\caption{IGRINS Orders $73-93$.  Note that the $y-$axis is on a logarithmic scale.  }
	\label{fig:Kband3x7}
\end{figure*}
